%-------------------------
%  in Latex
% License : MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt} 
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1.4cm, top=0.8cm, right=1.2cm, bottom=1cm}
% Adjust margins
%\addtolength{\oddsidemargin}{-0.5in}
%\addtolength{\evensidemargin}{-0.5in}
%\addtolength{\textwidth}{1in}
\usepackage[most]{tcolorbox}
\tcbset{
	frame code={}
	center title,
	left=0pt,
	right=0pt,
	top=0pt,
	bottom=0pt,
	colback=gray!20,
	colframe=white,
	width=\dimexpr\textwidth\relax,
	enlarge left by=-2mm,
	boxsep=4pt,
	arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{:\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1},\hspace{0.3mm}#2 & \textit{\small{#3}} 
    \end{tabular*}
    \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} &  \footnotesize{#2}\\
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeProject}[4]{
\vspace{0.5mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#3}} \\
        \footnotesize{\textit{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-2.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
% \renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm]}
\newcommand{\resumeHeadingSkillStart}{\begin{itemize}[leftmargin=*,itemsep=1.7mm, rightmargin=2ex]}
\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{2mm}}
\newcommand{\resumeHeadingSkillEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-2mm}}
\newcommand{\cvsection}[1]{%
\vspace{2mm}
\begin{tcolorbox}
    \textbf{\large #1}
\end{tcolorbox}
    \vspace{-4mm}
}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Ajay Chanumolu} % Your Name
\newcommand{\course}{B.Tech - (2022-26)} % Your Course
\newcommand{\phone}{8074177736} % Your Phone Number
\newcommand{\emailb}{chanumoluajay@gmail.com} %Email 2
\newcommand{\linkedin}{ajaychanumolu} %linkedin



\begin{document}
\fontfamily{cmr}\selectfont
%----------HEADING-----------------

{
\begin{tabularx}{\linewidth}{L r}
  \textbf{\LARGE \name} 
  \\ \course & +91-\phone\\ 
  {Artificial Intelligence \& Machine Learning } & \href{mailto:\emailb}{\emailb}
  \\{Sagi Ramakrishnam Raju Engineering College} & \href{https://www.linkedin.com/in/\linkedin/}{linkedin.com/in/\linkedin}
\end{tabularx}
} 

\section{Education}
\setlength{\tabcolsep}{5pt} % Default value: 6pt
% \renewcommand{\arraystretch}{1.1} % Default value: 1
\small{\begin{tabularx}
{\dimexpr\textwidth-3mm\relax}{|c|C|c|c|}
  \hline
  \textbf{Degree/Certificate } & \textbf{Institute/Board} & \textbf{CGPA/Percentage} & \textbf{Year}\\
  \hline
  B.Tech. AI\&ML & SRKR Engineering College& 8.69 & Till-3-2\\

 %Optional
  \hline
  Senior Secondary & APBIE Board & 88\% & 2020-22 \\
  \hline
  Secondary & CBSE Board & 77\% & 2020 \\
  \hline
\end{tabularx}}
\vspace{-2mm}

\section{Experience}

\resumeProject
  {SDE Intern, Truviq Systems} % Role & Company
  {AI-Powered Recruitment Automation} % Focus area
  {May 2025 – Present} % Duration

  \resumeItemListStart
    \item {Built an end-to-end automation pipeline using \textbf{n8n} to streamline LinkedIn candidate sourcing based on dynamic job descriptions.}
    \item {Integrated \textbf{Apify APIs} for large-scale LinkedIn profile scraping and filtering using custom role-specific parameters.}
    \item {Implemented \textbf{LLM-based semantic matching models} (e.g., Gemini) to rank candidate-job relevance and trigger automated email outreach for high-fit profiles.}
  \resumeItemListEnd


    \resumeProject
  {Cloud Intern, Takshalabs} % Role & Company
  {Cloud Deployment} % Project/Team or Division
  {Feb. 2024 – May. 2024} % Duration

  \resumeItemListStart
    \item {Deployed a PHP-based web application on an Azure Virtual Machine, configuring the cloud environment for seamless performance and secure access.}
  \resumeItemListEnd


    \vspace{-3mm}

\section{Projects}
\resumeSubHeadingListStart
   \resumeProject
  {DeepTrace: Multi-Modal Deepfake Detection} % Project Name
  {Deep Learning} % Category
  {Jan. 2024} % Dates
  {\href{https://github.com/ajaychanumolu/DeepTrace}{GitHub}} % GitHub Link

  \resumeItemListStart
    \item {Built a deepfake detection system using ResNeXt+LSTM for video (accuracy: 83\%), CNN for audio (accuracy: 96\%), and DenseNet121 for images (accuracy: 99.4\%). \\ \textbf{Stack:} Python, PyTorch, TensorFlow, OpenCV, Jupyter}
  \resumeItemListEnd

    
    \resumeProject
  {Sclerosis Disease Prediction} % Project Name
  {Machine Learning } % Category
  {Dec. 2024} % Dates
  {\href{https://github.com/ajaychanumolu/Sclerosis_Disease_Prediction}{GitHub}} % GitHub Link

  \resumeItemListStart
   \item {Developed a Random Forest Classifier with RFE and hyperparameter tuning to predict sclerosis progression with 87.2\% accuracy, evaluated using ROC-AUC.}
\item {\textbf{Stack:} Python, Scikit-learn, Pandas, Gradio, Matplotlib}
  \resumeItemListEnd
 \resumeProject
  {Chat with PDF using AI} % Project Title
  {Document Query Automation} % Project Category
  {May 2025} % Duration
  {\href{https://github.com/ajaychanumolu/Chat-with-PDF-using-AI-n8n-Workflow}{GitHub}} % GitHub Link

  \resumeItemListStart
    \item {Built a workflow to extract PDF content, embed it using Gemini, and store in Pinecone for AI-based question answering.}
    \item {Stack: n8n, Gemini API, Pinecone, Google Drive}
  \resumeItemListEnd


    
   \resumeProject
  {AI-Powered Tweet Summarizer} % Project Title
  {Social Media Intelligence} % Project Category
  {June 2025} % Duration
  {\href{https://github.com/ajaychanumolu/tweet-summarizer-n8n}{GitHub}} % GitHub Link

  \resumeItemListStart
   \item {Built a no-code workflow to extract Tweets, summarize with Gemini, analyze sentiment, and save results in Google Sheets.}
    \item {Stack: n8n, Apify, Gemini API, Google Sheets}
  \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-5.5mm}


\section{Technical Skills}
 \resumeHeadingSkillStart
  \resumeSubItem{Programming} % Category
    {Java, Python(familiar)}
\resumeSubItem{Development} % Category
    {Gradio, Streamlit, HTML, CSS, JavaScript}

    \resumeSubItem{Automation Tools} % Category
    {n8n (workflows, webhooks, APIs, data pipelines)}

        \resumeSubItem{CS Subjects} % Category
    { Data structures and Algorithms, OOPs concepts, Operating system}

            \resumeSubItem{Deep learning} % Category
    { Familiar with Tensorflow, Keras, Standard Deep learning models and concepts}
\hspace{3mm}
 \resumeHeadingSkillEnd


% \section{Key courses taken}
% \resumeHeadingSkillStart
%  \resumeSubItem{Mathematics} % Category
%     {Calculus, Linear Algebra and Ordinary Differential Equation\-I, Complex Analysis and Differential Equations-II, Numerical Methods.}
% \resumeSubItem{Computer Science}
%  {Computer Programming, Discrete Mathematical Structures, Data Structures and Algorithms, Data Base \& Information Systems, Computer Vision, Crypotography}
% %  \resumeSubItem{Electrical and Electronics} % Category
% %     {Advanced Control Systems, Digital Systems, Microprocessors} % Skills
%  \resumeHeadingSkillEnd


\section{Positions of Responsibility}
\vspace{-0.4mm}
\resumeSubHeadingListStart
\resumePOR{Executive Body Member} % Position
    { Association of Computer Engineers Club, SRKREC} %Club,Event
    {Aug. 2024 - Aug. 2025} %Tenure Period
\resumePOR{Android Core Team Member} % Position
    { GDSE, SRKREC} %Club,Event
    {Aug. 2023 - Sep. 2024} %Tenure Period
\resumeSubHeadingListEnd
\vspace{-4mm}


\section{Certifications}
\vspace{-0.2mm}
\resumeSubHeadingListStart

  \resumePOR{Java Programming Fundamentals}{GalileoX (edX)}{2024}
  \resumePOR{Postman API Fundamentals Student Expert}{Postman}{2024}

\resumeSubHeadingListEnd


\resumeSubHeadingListEnd

% \vspace{-2mm}
\hspace*{-5mm}\rule{1.035\textwidth}{0.1mm}


%-------------------------------------------
\end{document}


